Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics 

### 2020-05-04 Final-Draft.Rmd
plots

Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
day_initial<- as.Date("2020-03-14")
day_final<- as.Date("2020-03-21")
Finaldata<- Finaldata%>%
  filter(Day>=day_initial)%>%
  filter(Day<=day_final)
```

@@

@@

grid.arrange(p1,p2)

```
Our first visualization is looking at the percent of residents that identify as white within the United States compared to those whom identify as asian. As you can see, there is a higher percent of white identifying residents overall but most specifically in the Midwest and northeast states. In regards to Asian-Americans, there is practically less than .1% per state with the exception of California and New York. From this visualization we can also see that places like Texas, California, and New Mexico have much lower white identifying residents which could provide important information for us in our actual analysis.

@@

ggplotly(e)
```
During the 2020-03-14 - 2020-03-21 week, Trump in an official press announcement labeled the Corona Virus as "China Virus" and we wanted to see how his comments affected search patterns across states.

>>>>

Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
day_initial<- as.Date("2020-03-14")
day_final<- as.Date("2020-03-21")
Finaldata<- Finaldata%>%
  filter(Day>=day_initial)%>%
  filter(Day<=day_final)

names(Finaldata)
```

@@

ggplotly(p1)

@@

ggplotly(p2)

```

Our first visualization is looking at the percent of residents that identify as white within the United States compared to those whom identify as asian. As you can see, there is a higher percent of white identifying residents overall but most specifically in the Midwest and northeast states. In regards to Asian-Americans, there is practically less than .1% per state with the exception of California and New York. From this visualization we can also see that places like Texas, California, and New Mexico have much lower white identifying residents which could provide important information for us in our actual analysis.

@@

e
```

During the 2020-03-14 - 2020-03-21 week, Trump in an official press announcement labeled the Corona Virus as "China Virus" and we wanted to see how his comments affected search patterns across states.
